\begin{newenv}{Acknowledgements}
This dissertation marks the end of an exciting journey. I would like to express my deepest gratitude to a number of people that accompanied me during this time. 

My deepest appreciation goes to my supervisor Dr. Tristan Bereau, who supported me with his unlimited energy, his countless ideas and his ability to motivate and excite everyone around him. I enjoyed the freedom Tristan gave my in my research and his guidance whenever I needed it.   

I am deeply grateful to Prof. Dr. Kurt Kremer to accept me in his group at the Max Planck Institute for Polymer Research in Mainz. I appreciate his ability to give short lectures on any topic and always supporting me with his deep insight.

Special thanks to Prof. Dr. Evert Jan Meijer who became my second supervisor at the University of Amsterdam and supported me in the last chapter of my journey. I also thank the other members of my doctorate committee: Prof. Dr. Peter Bolhuis, Prof. Dr. Daniel Bonn, Prof. Dr.~ir. Marjolein Dijkstra, and Dr. Edan Lerner. 

I want to thank my colleagues for the countless discussion. A special thanks go to Prof. Dr. Burkhard D\"{u}nweg for sharing his knowledge with me and suggesting literature whenever I asked and to Dr. Joseph Rudzinski for all the discussion and his great support. I thank Kiran, Svenja, Bernadette, Christoph, Dominik, Bin, Marta, Martin, Roberto, Clemens, Anton, Claudio, Omar, Yasemin, Manjesh, Robin, Nezhat, Hannah, Debashish, Artreyee, Arghya, Marc, Alessia, Chan, and Timon for a great time at the Max Planck Institute for Polymer Research.

I would like to express my deepest gratitude to Prof. Dr. Wolfhard Janke, Dr. Thomas Neuhaus, Paul Spitzner and Dr. Johannes Zierenberg who taught me and discussed with me before and during my time in Mainz. 

Lastly I thank my brothers and my parents. Your unconditional support is the constant in my life and I am lucky to have such a great family. 


\end{newenv}
